Compare findings

### 2017-06-05 Code/validation/5 SH_second_comparison.Rmd
reconfig and new file

---
title: "Compare findings"
output: github_document
---

@@

```{r}
ggplotly(ggplot(compare.le, 
       aes(x = le.gap.width.SH, y = le.gap.width)) +
  geom_point(aes(col = state)) +
  facet_grid(year ~ sex) +
  geom_abline(intercept = 0, slope = 1) + 
  ylab("Width of CI for LE gap") +
  xlab("Original width of CI for LE gap") )
```

**OLD**
**Figure 2: Comparison of life expectancy change over time (1990 vs. 2009) between the original model and our model**

```{r}
ggplot(compare.le, 
       aes(x = le.white.original, y = le.white)) +
  geom_point(aes(x = le.black.original, y = le.black, col = "blacks")) + 
  geom_point(aes(col = "whites")) +
  facet_grid(~sex ) +
  geom_abline(intercept = 0, slope = 1) + 
  ylab("Life expectancy change (years)") +
  xlab("Original life expectancy change (years)") +
  geom_text(data = subset(compare.le, small.black.state == T & year == "difference"),
            aes(x = le.black.original, y = le.black, label = state), size = 2.5)

```

**Figure 4: Comparison of change over time (1990 vs. 2009) in the life expectancy gap between the original model and our model**

```{r}
ggplot(subset(compare.le, state!= "Wyoming" & year == "difference"), 
       aes(x = le.gap.original, y = le.gap)) +
  geom_point() +
  facet_grid(.~sex ) +
  geom_abline(intercept = 0, slope = 1) + 
  ylab("Change in life expectancy gap (years)") +
  xlab("Original change in life expectancy gap (years)") +
  geom_text(data = subset(compare.le, small.black.state == T & year == "difference"),
            aes(x = le.gap.original, y = le.gap, label = state), size = 2.5)
```

**Figure 6: Comparison of the change over time (1990 vs. 2009) in the CI width for LE gap between the original model and our model**

```{r}
ggplot(subset(compare.le, state!= "Wyoming" & year == "difference"), 
       aes(x = le.gap.width.original, y = le.gap.width)) +
  geom_point() +
  facet_grid(.~sex ) +
  geom_abline(intercept = 0, slope = 1) + 
  ylab("Width of CI for LE gap") +
  xlab("Original width of CI for LE gap") +
  geom_text(data = subset(compare.le, small.black.state == T & year == "difference"),
            aes(x = le.gap.width.original, y = le.gap.width, label = state), size = 2.5)
```

>>>>

---
title: "Compare findings"
output: html_document
---

In this file we compare our findings (using our data which is different because higher rate of missingness and more years of data) to Sam's Health Affairs appendix data.

@@

```{r}
ggplotly(ggplot(compare.le, 
       aes(x = le.gap.width.SH, y = le.gap.width)) +
  geom_point(aes(col = state)) +
  facet_grid(year ~ sex) +
  geom_abline(intercept = 0, slope = 1) + 
  ylab("Width of CI for LE gap") +
  xlab("Width of CI for LE gap from Health Affairs paper") )
```
